The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2023-12-16 r_r/manuscript_rihe_r_r.Rmd
updates to figures

Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-comp-privu-privhs-pubhs) address research question 3, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?" Additionally, Appendix Figures \@ref(fig:enroll-pubu-privu) and \@ref(fig:enroll-pubu-privhs-pubhs) show the 12th grade enrollment size of visited high schools.

@@

Finally, Figure X examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample. Figure X does the same for selective private universities. These figures are motivated by the finding that many universities in our sample visited a large number of private schools in the South, where private school enrollment growth has been the strongest [@RN4504]. For public research universities, Figure X shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools. This was true for all public universities in our sample, and particularly for UNIVERSITY X, Y, Z. Results for selective private universities in Figure X mirror the results for public research universities. Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits. 
<!--TODO: Supplemental figures \@ref(fig:race-comp-pubu-privhs-pubhs) AND \@ref(fig:race-comp-privu-privhs-pubhs) are now moved to appenidix-->
INSERT FIGURES X AND X ABOUT HERE

@@

Across the universe of private high schools, most schools enroll relatively few students who identify as Black, Latinx, or Native. For the public and private universities in our sample, the set of visited private schools enrolled fewer Black, Latinx, and Native students than the national universe of private schools. By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native. <!--TODO: [ADD A SENTENCE ABOUT RACIAL COMPOSITION OF VISITS TO SOUTH?]-->

@@

@@

```{r race-comp-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs. visited private high schools in the South, public research universities"}
include_graphics(file.path(figures_dir, 'race_comp_pubu_privhs_pubhs.pdf'))
```

@@

```{r race-comp-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs. visited private high schools in the South, selective private universities"}
include_graphics(file.path(figures_dir, 'race_comp_privu_privhs_pubhs.pdf'))
```

>>>>

Figures \@ref(fig:region-pubu-privu) through \@ref(fig:south-race-privu-privhs-pubhs) address research question 3, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?" Additionally, Appendix Figures \@ref(fig:enroll-pubu-privu) and \@ref(fig:enroll-pubu-privhs-pubhs) show the 12th grade enrollment size of visited high schools.

@@

Finally, Figure \@ref(fig:south-race-pubu-privhs-pubhs) examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample. Figure \@ref(fig:south-race-privu-privhs-pubhs) does the same for selective private universities. These figures are motivated by the finding that many universities in our sample visited a large number of private schools in the South, where private school enrollment growth has been the strongest [@RN4504]. For public research universities, Figure \@ref(fig:south-race-pubu-privhs-pubhs) shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools. This was true for most public universities in our sample, and particularly for the University of Georgia, University of South Carolina, and University of Cincinnati. A notable exception is SUNY Stony Brook, though this university only visited 12 private universities in the South. Results for selective private universities in Figure \@ref(fig:south-race-privu-privhs-pubhs) (with the exception of Marquette) mirror the results for public research universities. Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits. Appendix Figures \@ref(fig:south-race-comp-pubu-privhs-pubhs) and \@ref(fig:south-race-comp-privu-privhs-pubhs) show the full racial composition of visited public and private schools in the South.

INSERT FIGURES \@ref(fig:south-race-pubu-privhs-pubhs) AND \@ref(fig:south-race-privu-privhs-pubhs) ABOUT HERE

@@

Across the universe of private high schools, most schools enroll relatively few students who identify as Black, Latinx, or Native. For the public and private universities in our sample, the set of visited private schools enrolled fewer Black, Latinx, and Native students than the national universe of private schools. By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native. This is true of the visits to schools in the South as well.

@@

```{r south-race-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools in the South vs. visited private high schools in the South, public research universities"}
include_graphics(file.path(figures_dir, 'south_race_pubu_privhs_pubhs.pdf'))
```

```{r south-race-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools in the South vs. visited private high schools in the South, selective private universities"}
include_graphics(file.path(figures_dir, 'south_race_privu_privhs_pubhs.pdf'))
```

@@

```{r south-race-comp-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools in the South vs. visited private high schools in the South, public research universities"}
include_graphics(file.path(figures_dir, 'south_race_comp_pubu_privhs_pubhs.pdf'))
```

@@

```{r south-race-comp-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools in the South vs. visited private high schools in the South, selective private universities"}
include_graphics(file.path(figures_dir, 'south_race_comp_privu_privhs_pubhs.pdf'))
```
